Continuous gravitational waves in the lab: recovering audio signals with a table-top~optical microphone

### 2021-08-31 paper/ifo-appendix.tex
adding JKS reference

The likelihood is proportional to the probability of observing the data given an assumed model of the signal~\cite{Jaynes:2003}.
In this example the model is given by Eqn.~\ref{eqn:GNmodel}.
Under the assumption of Gaussian noise, the log-likelihood is 
\begin{equation}
\log \mathcal{L} = -\frac{1}{2}\ip{n}{n}\,, 
\end{equation}
where we define the inner product between $u(t)$ and $v(t)$ as $\ip{u}{v} = \int_0^T \mathrm{d} t \, u(t) v(t) $ and $T$ is the total time of the data. 
% We replace $n$ by $x-s$ (Eqn.~\ref{eqn:GNdata}), so that 
Using Eqns.~\ref{eqn:GNdata} and~\ref{eqn:GNmodel}, we find that
\begin{eqnarray}
\log \mathcal{L} &=& -\frac{1}{2}\ip{x-s}{x-s}\,, \\ 
                 &=& -\frac{1}{2}\ip{x}{x} - \frac{A^2}{2} \ip{\cos[\omega t + \phi]}{\cos[\omega t + \phi]} \nonumber\\
                 &&+ A \ip{x}{\cos[\omega t + \phi]}\,,\\ 
                 &=& -\frac{1}{2}\ip{x}{x} - \frac{A^2}{4} + A \ip{x}{\cos[\omega t + \phi]}\,,\label{eqn:logLike}
\end{eqnarray}

>>>>

The likelihood is proportional to the probability of observing the data given an assumed model of the signal~\cite{Jaynes:2003}.
In this example the model is given by Eqn.~\ref{eqn:GNmodel}.
Under the assumption of Gaussian noise, the log-likelihood is 
\begin{equation}
\log \mathcal{L} = -\frac{1}{2}\ip{n}{n}\,, 
\end{equation}
where we define the inner product between $u(t)$ and $v(t)$ as $\ip{u}{v} = \frac{1}{T} \int_0^T \mathrm{d} t \, u(t) v(t) $ and $T$ is the total time of the data~\cite{JKS:1998}. 
% We replace $n$ by $x-s$ (Eqn.~\ref{eqn:GNdata}), so that 
Using Eqns.~\ref{eqn:GNdata} and~\ref{eqn:GNmodel}, we find that
\begin{eqnarray}
\log \mathcal{L} &=& -\frac{1}{2}\ip{x-s}{x-s}\,, \\ 
                 &=& -\frac{1}{2}\ip{x}{x} - \frac{A^2}{2} \ip{\cos[\omega t + \phi]}{\cos[\omega t + \phi]} \nonumber\\
                 &&+ A \ip{x}{\cos[\omega t + \phi]}\,,\\ 
                 &=& -\frac{1}{2}\ip{x}{x} - \frac{A^2}{4} + A \ip{x}{\cos[\omega t + \phi]}\,,\label{eqn:logLike}
\end{eqnarray}
